Results

### 2025-06-13 notebooks/00_index.qmd
fig: update

```{julia}
using Dates
using Speasy
using DrWatson
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using Discontinuity
using SPEDAS
using DataFrames, DataFramesMeta
using GLMakie
using SPEDAS: set_meta, set_meta!
using PartialFunctions

@@

```{julia}
df, configs = workload()

@@

```{julia}
function plot_candidate(f, event, config, toffset=Second(0); kwargs...)
    tmin, tmax = event.t_us_ds
    t0 = tmin - toffset
    t1 = tmax + toffset

@@

    B_mva = mva(B, B) |> set_meta(; labels=𝑳.B_LMN)
    Va = Alfven_velocity_ts(B_mva, n) .|> u"km/s" |> set_meta(; labels=𝑳.Va_LMN, ylabel="V")
    V_mva = mva(V, B) |> set_meta(; labels=𝑳.V_LMN)
    J = hcat(current_density(B_mva, V_mva)...) |> set_meta(; labels=𝑳.J, ylabel="J")

    result = [tnorm_combine(B_mva), tsubtract(V_mva), n, tsubtract(Va), J]

@@

f = Figure(; size=(1200, 800))
res_psp = plot_candidate(f[1, 1], psp_df[18, :], psp_config, Second(10))
# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_config)
# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_config, Second(10))
f

@@

@@

```{julia}
using AlgebraOfGraphics
using Discontinuity: compute_params!, filter_low_mva_quality, compute_Alfvenicity_params!
using Beforerr
using Beforerr: add_labels!
using CairoMakie
using StatsBase
CairoMakie.activate!()

>>>>

```{julia}
using Dates
using Speasy
using DrWatson
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using Discontinuity
using Discontinuity: compute_params!, compute_Alfvenicity_params!, filter_low_mva_quality
using SPEDAS
using DataFrames, DataFramesMeta
using GLMakie
using SPEDAS: set_meta, set_meta!
using PartialFunctions

@@

```{julia}
df, configs = workload()
compute_params!(df)
compute_Alfvenicity_params!(df)

@@

```{julia}
function plot_candidate(f, event, config, toffset=Second(0); add_J=false, kwargs...)
    tmin, tmax = event.t_us_ds
    t0 = tmin - toffset
    t1 = tmax + toffset

@@

    B_mva = mva(B, B) |> set_meta(; labels=𝑳.B_LMN)
    Va = Alfven_velocity_ts(B_mva, n) .|> u"km/s" |> set_meta(; labels=𝑳.Va_LMN, ylabel="V")
    V_mva = mva(V, B) |> set_meta(; labels=𝑳.V_LMN)

    result = [tnorm_combine(B_mva), tsubtract(V_mva), tsubtract(Va)]

    if add_J
        J = hcat(current_density(B_mva, V_mva)...) |> set_meta(; labels=𝑳.J, ylabel="J")
        push!(result, J)
    end

@@

f = Figure(; size=(1200, 800))
psp_event = filter_low_mva_quality(psp_df)[4, :]
res_psp = plot_candidate(f[1, 1], psp_event, psp_config, Second(10))
@info "v_l_ratio" psp_event.v_l_ratio
# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_config)
# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_config)
# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_config, Second(10))
f

@@

<!-- TODO: add Alfvénicity over time -->

@@

```{julia}
using AlgebraOfGraphics
using Discontinuity: compute_params!, compute_Alfvenicity_params!
using Beforerr
using Beforerr: add_labels!
using CairoMakie
using StatsBase
CairoMakie.activate!()
